---
title: "p8105_hw_cl4469"
Author: Chen Liang
output: github_document
---

# Problem 1

###### Load the moderndive library, and use the following code to load the early_january_weather dataset:

```{r}
library(moderndive)
data("early_january_weather")
```

###### The following code loads the early_january_weather dataset and includes a description 

```{r} 
data_set <- data("early_january_weather")
```

###### Describing the Data Set 

```{r}
mean(early_january_weather$temp)
range(early_january_weather$temp)
median(early_january_weather$temp)
range(early_january_weather$humid)
mean(early_january_weather$humid)
range(early_january_weather$wind_speed)
```
This data set contains 358 observations of 15 variables,
including: origin, year, month, day, hour, temperature, dew,
humidity, wind direction, wind speed, wind
gust,precipitation, pressure, visibility.

Values for temperature range from 24.08 to 57.92, the mean
of temperature is 39.5821, median is 39.02. Values for
humidity range from 32.86 to 100, mean humidity is 65.4767.
Values for wind speee range from 0 to 24.14.

###### Describe the size of the dataset (using nrow and ncol)
```{r}
nrow(early_january_weather)
ncol(early_january_weather)
```

###### Describe the mean temperature
```{r}
mean(early_january_weather$temp)
```

###### Make a scatterplot of temp (y) vs time_hour (x)
```{r}
library(ggplot2)

ggplot(early_january_weather,aes(x=time_hour,y=temp, color=temp))+
  geom_point()+
  ggtitle("temperature vs. time_hour")+
  theme(plot.title = element_text(hjust = 0.5))

ggsave("scatterplot_temp vs. time_hour.pdf")
```
###### Describe this plot:
Temperatures are changing all the time, and in general, early
January is showing an upward trend. However, we can also
clearly see that the temperature is falling and then rising
on a daily basis, constantly repeating itself. In addition,
the day at the beginning of the month and the day in the
middle of the month the temperature drops significantly.

# Problem 2

```{r, results= FALSE}
library(dplyr)
```

###### Creat Sample data frame
```{r}
problem_df= tibble(
  vec_numeric = rnorm(10),
  vec_logical = vec_numeric > 0,
  vec_char = c("one", "two", "three", "four", "five", "six", "seven", "eight",
  "nine", "ten"),
  vec_factor = factor(c(rep("low",3),rep("medium",3), rep("high",4)))
)
```

###### Now, I try to take the mean of each variable in my data frame
```{r}
mean(problem_df)
mean(pull(problem_df, vec_numeric))
mean(pull(problem_df, vec_logical))
mean(pull(problem_df, vec_char))
mean(pull(problem_df, vec_factor))
```
The result shows that the mean of the numerical random 
sample vector (vec_numeric) and logical vector (vec_logical)
worked. However, some don't work. The mean of the character
vector (vec_char) and factor vector (vec_fac) shows that the
argument is not numeric or logical.

###### Thus, I will convert variables from one type to another.
```{r}
as.numeric(pull(problem_df, vec_logical))
as.numeric(pull(problem_df, vec_char))
as.numeric(pull(problem_df, vec_factor))
```
When we change these variables into numerics, logical vector
can be changed into a numeric vector with 0's and 1's, this
is because the data of number vector is True or False, which
can converted to numeric of 0's and 1's.

And also, the factor vector can be changed into a numeric
vector with 1, 2, and 3, this is because "low""medium"
"high" can be explained by each level of number. But there
is no meaningful statistic to describe the 3 levels if we 
take the mean of numeric factor, so this will not help to 
explain taking a mean.

However, if we convert vec_char into numeric vector, there 
is a warning message: NAs introduced by coercion. Since 
there is no logical way to put a number to these character 
vector, mean cannot be found.

