---
title: "Simple document"
output: pdf_document
---

# Problem 1

Load the moderndive library, and use the following code to load the early_january_weather dataset:

```{r}
library(moderndive)
data("early_january_weather")
```

The following code loads the early_january_weather dataset and includes a description 

```{r} 
data_set <- data("early_january_weather")
```

Describing the Data Set 

```{r}
mean(early_january_weather$temp)
range(early_january_weather$temp)
median(early_january_weather$temp)
mean(early_january_weather$temp)
range(early_january_weather$humid)
range(early_january_weather$wind_speed)
```
This dataset contains 358 observations of 15 variables, including: origin, year, month, day, hour, temperature, dew, humidity, wind direction, wind speed, wind gust,precipitation, pressure, visibility.
Values for temperature range from 24.08 to 57.92, the mean of temperature is 39.5821.



```{r}
typeof(early_january_weather)
data_set_vector <- as.matrix(data_set)
nrow(early_january_weather)
ncol(early_january_weather)
mean(early_january_weather[["temp"]]) # or
mean(early_january_weather$temp)
```
